On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-04-20 Manuscript/manuscript.tex

The remainder of the papers is organized as follows:
The Block Bootstrap CIs section reviews how these intervals
are constructed as well as the general procedure for block bootstrap parameter
estimation. The Simulation Study section offers an explanation of the
simulation design and results. Finally, the Concluding Remarks section
discusses the main takeaways from the results, how these findings could be
useful, and possible future explorations.

\section{Block Bootstrap CIs}
\label{sec:blkbootreview}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then aligning them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$):

\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
    \end{cases}
\end{equation}

The second implementation of moving block bootstrap was used in
this study, and moving block bootstrap in general had been found to yield the 
lowest error.
\citep{radovanov2014comparison}.  
\jy{what does the last sentence mean?} Addressed

The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

\subsection{Construct CIs}

@@

\paragraph{Percentile CI}
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
%% Not the right place
%% This interval works well when attempting to recover the mean and
%% standard deviation of a temporally dependent process, but its coverage of
%% the temporal dependence deteriorates as $n$ increases.

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2},
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered by the point estimator $\hat\theta_n$ and is
asymmetric, as different critical values are used to compute
the lower and upper bounds.
\jy{Define $\delta^*$?} Addressed
\jy{Say a few words about its properties} Addressed

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
In this study, the BCA CI is an interval centered at the point estimator.
Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat\theta_{BCA}[\alpha/2],
\hat\theta_{BCA}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.

\section{Simulation Study}
\label{sec:simstudy}

@@

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased. $n =$
100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

@@

\section{Concluding Remarks}
\label{sec:conremarks}

@@

BBOB
B

>>>>

The remainder of the papers is organized as follows.
Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
bootstrap estimates construct CIs. Section~\ref{sec:simu} reports a simulation
study comparing the coverage rates of the block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

\section{Block Bootstrap CIs}
\label{sec:bbci}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then aligning them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$):
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}

\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
The second implementation of moving block bootstrap was used in
this study, and moving block bootstrap in general had been found to yield the 
lowest error \jy{state we use it because it is implemented in package boot and
  cite boot}
\citep{radovanov2014comparison}.  
\jy{This reference is from a low-tier journal. Find something from a stronger journal?}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

\subsection{Bootstrap CIs}

@@

\jy{can we give references to each of the method? How about the review paper in
  Statistical Science?}

\paragraph{Percentile CI}
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
As will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is in
contrary to what one would expect.

\paragraph{Centered Percentile CI}
Centered percentile CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\delta$, the difference between a point estimate and
$\bar\theta_n^{(b)}$. For $b \in \{1, \ldots, B\}$, we can obtain a
$\delta^{(b)}$ based on the $b$th bootstrap point estimate. Let
$\delta_{\alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\delta^{(1)}, \ldots,  \delta^{(B)}\}$.  
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat{\theta}_{n} + \delta^{(b)}_{\alpha/2}, \quad
\hat{\theta}_{n} + \delta^{(b)}_{1 - \alpha/2}).
\]
This CI is necessarily centered by the point estimator $\hat\theta_n$ and is
asymmetric, as different critical values are used to compute
the lower and upper bounds.

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
In this study, the BCA CI is an interval centered at the point estimator.
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$
A $(1 - \alpha)$ centered percentile CI is
\[
(\hat\theta_{BCA}[\alpha/2], \quad
\hat\theta_{BCA}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
\jy{why is it called BCA?}

\section{Simulation Study}
\label{sec:simu}

@@

If $\theta$ is not covered at that $n$, a larger $n$ may be
necessary, assuming that performance will improve as $n$ is increased. $n =$
\jy{learn from how I presented this}
100, 200, 300, 400, and 500, 600, 700 were used in this study. Remember that
the goal of this study is to find the smallest $n$ which is sufficient for
proper coverage.

@@

\section{Discussion}
\label{sec:disc}

@@
